oREVIRT analysis

### 2022-11-09 analysis/irt_analysis.Rmd
run rasch + guessing

```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(tidyboot)
library(brms)
library(readxl)
library(ggthemes)
library(geomtextpath)
library(coda)
library(ggridges)

@@

```{r}
mc1 <- loo_compare(irt1, irt1_guess, irt2, irt3)%>%as_tibble(rownames = "model")

@@

```{r}
mc_dif_rasch <- loo_compare(irt1_sel, irt1_dif_sex_sel, irt1_dif_order_sel)%>%as_tibble(rownames = "model")

write_csv(mc_dif_rasch, "../saves/model_comparison_dif_rasch_sex.csv")
```

@@

```
```{r}
ggsave("../graphs/dif_cor.png", height = 8, width = 8, scale = 1.2)
```

@@

@@

```{r}
loo_compare(irt1_guess_sel, irt3_sel)%>%as_tibble(rownames = "model")

@@

```{r}
rel_dat <- irt_dat%>%
  select(-sex, -order)%>%
  filter(targetWord %in% sel_items_rasch)%>%
  group_by(subjID)%>%
  distinct(targetWord, .keep_all = T)%>%
  pivot_wider(names_from = targetWord, values_from = correct)%>%
  ungroup()%>%
  select(-subjID)

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(tidyboot)
library(brms)
library(readxl)
library(ggthemes)
library(geomtextpath)
library(coda)
library(ggridges)
library(testing)

@@

```{r}
mc1 <- loo_compare(irt1, irt1_guess, irt3)%>%as_tibble(rownames = "model")

@@

@@

```{r}
ggsave("../graphs/dif_cor.png", height = 8, width = 8, scale = 1.2)
```

@@

```{r}
loo_compare(irt1_guess_sel, irt1_guess_dif_order_sel, irt1_guess_dif_sex_sel)%>%as_tibble(rownames = "model")

```{r}
dif_sex_guess <- as_draws_df(irt1_guess_dif_sex_sel)%>%
  select(b_eta_Intercept, starts_with("r_targetWord"))%>%
  mutate(iter = 1:n()) %>%
  pivot_longer(starts_with("r_targetWord")) %>%
  mutate(name = str_remove(name, pattern = "r_targetWord__eta"),
         name = str_remove_all(name, pattern = "\\[|\\]"))%>%
  separate(name, into = c("item", "sex"), sep = "\\,")%>%
  mutate(sex = str_remove(sex, pattern = "sex"),
         val =  value)%>%
  group_by(item, sex)%>%
  summarise(mode = estimate_mode(val),
            uci = hdi_upper(val),
            lci = hdi_lower(val))%>%
  left_join(aoa%>%rename(item = targetWord))

saveRDS(dif_sex_guess, "../saves/model_params_irt1_guess_dif_sex.rds")

dif_sex_guess <- readRDS("../saves/model_params_irt1_guess_dif_sex.rds")

ggplot(dif_sex_guess,aes(x = reorder(item, aoa_german_comb))) +
	geom_point(aes(col = sex, y = lci), position = position_dodge(width = .5)) +
  geom_point(aes(col = sex, y = uci), position = position_dodge(width = .5)) +
  geom_linerange(aes(col = sex, ymin = lci + 0.1, ymax = uci-0.1), position = position_dodge(width = .5), alpha = .5) +
	coord_flip() +
  scale_color_colorblind(labels = c("male","female"), name = "Group")+
	labs(x = "Item", y = "Easiness estimate")+
  theme_few()
```

```{r}
dif_sex_guess%>%
  pivot_wider(names_from = sex, values_from = c(mode,uci,lci))%>%
  ggplot(., aes(x = mode_f, y = mode_m))+
  geom_abline(intercept = 0, slope = 1, lty = 1, alpha = .75)+
  geom_point(pch = 1, size = 2, stroke  = 1, aes(col = factor(aoa_german_comb)))+
  geom_linerange(aes(ymin = lci_m, ymax = uci_m),  alpha = .25, lty = 1)+
  geom_linerange(aes(xmin = lci_f, xmax = uci_f),  alpha = .25, lty = 1)+
  geom_text(aes(label = item, x = uci_f +0.2))+
  labs(x = "Group: female", y = "Group: male")+
  scale_color_viridis_d()+
  guides(col = F)+
  theme_few()

```{r}
ggsave("../graphs/dif_cor.png", height = 8, width = 8, scale = 1.2)
```

@@

```{r}
loo_compare(irt1_guess_sel, irt3_sel, criterion = "waic")%>%as_tibble(rownames = "model")%>%
  left_join(loo_compare(irt1_guess_sel, irt3_sel, criterion = "loo")%>%as_tibble(rownames = "model")%>%select(model, elpd_loo, se_elpd_loo, p_loo, se_p_loo, looic, se_looic))
```

@@

```{r}
rel_dat <- irt_dat%>%
  select(-sex, -order)%>%
  filter(targetWord %in% rasch_selected_items)%>%
  group_by(subjID)%>%
  distinct(targetWord, .keep_all = T)%>%
  pivot_wider(names_from = targetWord, values_from = correct)%>%
  ungroup()%>%
  select(-subjID)
